---
output: html_document
---
  
#### Predictors

**Candidate predictors**
The predictors are determined using data recorded relative to the target cohort index date.  The settings `endDays` specifies the number of days relative to the target index that is the latest point in time for determining the covariates.  For example, an `endDays` of -1 means that no data recorded on index or after are used by the covariates (the covariates only use data recorded up to index-1 day).

```{r, echo=FALSE, results = 'asis'}
if(class(modelDesignSetting$covariateSettings) == 'covariateSettings'){
  modelDesignSetting$covariateSettings <- list(modelDesignSetting$covariateSettings)
}
cat('\n There are ', length(modelDesignSetting$covariateSettings), ' covariate settings. \n')
for(j in 1:length(modelDesignSetting$covariateSettings)){
  
   cat('\n Covariate Setting', j, '\n')
  
  covariateDetails <- formatCovariateSettings(modelDesignSetting$covariateSettings)
  
  
print(
  shiny::tagList(
  reportTableFormat(
    table = covariateDetails, 
    groupBy = 'input',
    columns = defaultColumns(covariateDetails)
  )
  )
)
  cat('\n \n')
}
```

**Feature Engineering**
```{r, echo=FALSE, results = 'asis'}
if(class(modelDesignSetting$featureEngineeringSettings) == 'featureEngineeringSettings'){
  modelDesignSetting$featureEngineeringSettings <- list(modelDesignSetting$featureEngineeringSettings)
}
if(!is.null(attr(modelDesignSetting$featureEngineeringSettings[[1]],"fun"))){
  if(attr(modelDesignSetting$featureEngineeringSettings[[1]],"fun") != 'sameData'){
  
    cat('\n There are ', length(modelDesignSetting$featureEngineeringSettings), ' feature engineering settings. \n')
    for(i in 1:length(modelDesignSetting$featureEngineeringSettings)){
  
      cat('\n The function ', attr(modelDesignSetting$featureEngineeringSettings[[i]],"fun"), ' with inputs: \n')
      feData <- data.frame(
        name = names(modelDesignSetting$featureEngineeringSettings), 
        value = unlist(lapply(modelDesignSetting$featureEngineeringSettings, function(x) paste(x, sep = '', collapse='-')))
        )
  
      print(
        reportTableFormat(
    table = feData , 
    caption = paste('feature engineering setting ', i)
  )
  )
      cat('\n \n')
  
    }
  } else{
  cat('\n None \n')  
  }
} else{
  cat('\n None \n')  
}
```

**Pre-processing**

The following pre-processing were applied:


```{r, echo=FALSE, results = 'asis'}
if(modelDesignSetting$preprocessSettings$normalize){
  cat('\n - The data were normalized using the formula: value/maxValue . \n')
}
if(modelDesignSetting$preprocessSettings$minFraction > 0){
  cat('\n - Candidate predictors occuring in less than ', modelDesignSetting$preprocessSettings$minFraction*100,'\\% of patients in the target population were removed. \n')
}
if(modelDesignSetting$preprocessSettings$removeRedundancy){
  cat('\n - Candidate predictors that were redundant (completely correlated with another predictor) were removed.  When two predictors are completely correlated, the most common predictor is removed.  For example, if 60\\% of the target population were male and 40\\% were female, then the male gender predictor would be removed since it is redundant and more common. \n')
}
```