---
output: html_document
---
  
##### Analysis

The model that will be trained is a ``r attr(modelDesignSetting$modelSettings$param,'settings')$name `` that uses the `PatientLevelPrediction` function ``r modelDesignSetting$modelSettings$fitFunction `` to fit the model.

```{r, echo=FALSE}
if(modelDesignSetting$modelSettings$fitFunction == "fitCyclopsModel"){
 parameters <- data.frame(
   name = names(modelDesignSetting$modelSettings$param),
   value = unlist(
     lapply(modelDesignSetting$modelSettings$param, function(x) paste(names(x), x, collapse = '-', sep=':'))
   )
 )
 
 settings <- data.frame(
   name = names(attr(modelDesignSetting$modelSettings$param,"settings")),
   value = unlist(
     lapply(
       attr(modelDesignSetting$modelSettings$param,"settings"), 
       function(x) paste0(names(x), x, collapse = ':', sep=' ')
            )
     )
 )
 row.names(settings) <- NULL
} else{
   parameters <- 
       do.call('rbind', lapply(
       modelDesignSetting$modelSettings$param, 
       function(x){
         unlist(lapply(x, function(x) paste0(x, sep=' ', collapse=':')))
       })
     )
 
 settings <- data.frame(
   name = names(attr(modelDesignSetting$modelSettings$param,"settings")),
   value = unlist(
     lapply(
       attr(modelDesignSetting$modelSettings$param,"settings"), 
       function(x) paste0(names(x), x, collapse = '-', sep='')
            )
     )
 )
 row.names(settings) <- NULL
}
```

**Cross-validation settings**

The cross validation settings are to use ``r modelDesignSetting$splitSettings$nfold `` folds in the training data that are partitioned using the ``r attr(modelDesignSetting$splitSettings,"fun") `` function and consist of ``r modelDesignSetting$splitSettings$train*100 `` \% of the complete data.  The seed used for splitting the data is ``r modelDesignSetting$splitSettings$seed ``.

**Hyper-parameter search**

The hyper-parameters investigated while fitting the model are listed below.  The combination of hyper-parameters that obtains the highest AUROC value in the training data via cross validation will be uses in the final model.

```{r, echo=FALSE, results='asis'}
print(
  reportTableFormat(
    table = parameters, 
    caption = paste('Hyper-parameters combinations searched to fit the model')
  )
)
```

**Other settings**

The other settings used to fit the model, such as seeds used for reproducibility, are:

```{r, echo=FALSE, results='asis'}
print(
  reportTableFormat(
    table = settings, 
    caption = paste('Other model fitting settings')
  )
)
```

**Internal validation**

The model will be assessed internally using a test set that consists of ``r modelDesignSetting$splitSettings$test*100`` \% of the complete data.