---
title: "Using ProtocolGenerator"
author: "Jenna Reps"
date: "`r Sys.Date() `"
output: html_document
vignette: >
  %\VignetteIndexEntry{guide}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

To run protocol generator you need to have a `Strategus` json specification (either as a saved file or loaded into R).  You can specify a `webAPI` to use for concept set extraction (note: rendered concept sets can change depending on the webAPI's vocab).  The `outputLocation` is where the protocol html file will be saved to.

You can personalize the protocol with the following inputs:

- protocolSubheading: this lets you specify a title for the study
- headerColor: this lets you specify a header color for the protocol (defaults to dark blue)
- headerLogoLocation: this lets you specify a logo to add to the protocol header (defaults to no logo)

To run the protocol generator using the demo json specification in the package you can run:

```{r demo, echo=TRUE, eval = FALSE, results = 'hide'}
library(ProtocolGenerator)

# to run the protocol generator with a demo json specification
test <- generateProtocol(
  jsonLocation = getDemoLoc(),
  webAPI = paste0('https://', 'api.ohdsi.org', '/WebAPI'),
  outputLocation = file.path(tempdir(), 'protocol'), 
  protocolSubheading = 'A demo protocol using the example specifcation json'
  #,headerColor = '4A1B12' # can optionally enter any HTML color code for the header
  #,headerLogoLocation = 'path to image' # can optionally add a logo to the header
)
```


