---
output: html_document
---

```{r, echo=FALSE, results = 'hide', include=FALSE}
library(CohortMethod)
package <- 'CohortMethod'

  # if authorise
  if(!is.null(params$authMethod)){
  ROhdsiWebApi::authorizeWebApi(
    baseUrl = params$webAPI, 
    authMethod = params$authMethod, 
    webApiUsername = params$webApiUsername, 
    webApiPassword = params$webApiPassword
      )
  }


cohortMethodSettings <- ProtocolGenerator::extractCohortMethodSettings(
  cohortMethodModuleSettings = cohortMethodModuleSettings,
    negativeControls = negativeControls,
    cohortDefinitionDf = cohortDefinitionDf
)

negativeControlsCM  <- cohortMethodSettings$negativeControlsCM
tcCombos <- cohortMethodSettings$tcCombos
outcomeRange <- cohortMethodSettings$outcomeRange
compIds <- cohortMethodSettings$compIds
targetParentsCount <- cohortMethodSettings$targetParentsCount
targetCohortCount <- cohortMethodSettings$targetCohortCount
tars <- cohortMethodSettings$tars
analysisCm <- cohortMethodSettings$analysisCm
cmOutUnique <- cohortMethodSettings$cmOutUnique
commonExclude <- cohortMethodSettings$commonExclude
nonCommonSets <-  cohortMethodSettings$nonCommonSets
commonNegativeId <- cohortMethodSettings$commonNegativeId
nonCommonNegSets <- cohortMethodSettings$nonCommonNegSets
diagSetting <- cohortMethodSettings$diagSetting 
refitPsForEveryOutcome <- cohortMethodSettings$refitPsForEveryOutcome
refitPsForEveryStudyPopulation <- cohortMethodSettings$refitPsForEveryStudyPopulation

```

## Cohort Method 

### Overview
::: {.callout-important collapse="false"}
# Summary of cohort method
Cohort method calculates comparative effect estimates.  It requires specifying a target cohort (treatment 1), comparator cohort (treatment 2) and the outcome of interest.  The standard process requires creating a propensity model to predict treatment and that is used to mimic randomization via matching, trimming or inverse probability weighting.  The method used to estimate the effect is specified via analysis settings. In addition, the user can specify negative controls to use for effect estimate calibration.

Using observational data for causal inference can be problematic due to various forms of potential bias.  To minimise bias effects, cohort method performs different diagostics that evaluate whether there is bias present and effect estimates are only unblinded if all diagnostics are passed.  For more details see [here](https://academic.oup.com/jamia/article/32/3/518/7950905).

```{r, echo=FALSE, results = 'asis'}
cat(paste0('In this specification there are ', targetParentsCount, ' unique parent target cohorts (corresponding to ', targetCohortCount, ' unique targets with subsets), see @sec-cm-tc.  There were between ', min(compIds$compCount),' and ', max(compIds$compCount), ' comparators per target cohort and ', outcomeRange, ' outcome/prior outcome lookbacks (see @sec-cm-out) per target cohort and comparator cohort pair. There are ', length(analysisCm), ' analyses settings specified, see @sec-cm-analyses. The ', length(tars), ' analyses time at risk settings are: '), tars, sep = '\n')
```
:::

### Combinations
```{r, echo=FALSE, results = 'asis'}

# gets just have one setting with all tcos - as works with bigger studies
cat(paste0('\n#### Target and Comparators {#sec-cm-tc}\n'))
cat('\n::: {.callout-important collapse="true"}\n')
cat('\n# Targets and comparators used in cohort method\n')
    
   cat("\n A relative effect for the risk of the outcome will be calculated for the target drug compared to the comparator drug for each target and comparator pair in the table below.",
           
           sep= '\n'
    )
  print(
    htmltools::tagList(
    reportTableFormat(
      table = tcCombos %>% dplyr::arrange(.data$parentNameTarget, .data$cohortNameComp),
      groupBy = "parentNameTarget", 
      groupByButton = TRUE,
      columns = ProtocolGenerator::cmColDef(
        elementId = "cm-tc-tab", 
        colNames = colnames(tcCombos)
          ),
    elementId = "cm-tc-tab"
    )
    )
  )
  cat('\n:::\n')
  
cat('\n#### Outcomes {#sec-cm-out}\n\n')
# add outcomes
for(cmi in 1:length(cmOutUnique)){
  cat(paste0('\n##### Outcome set ',cmi,' {#sec-cm-out-',cmi,'}\n\n'))
  cat('\n::: {.callout-important collapse="true"}\n')
  cat(paste0('\n# Outcome used in cohort method ', cmi, '\n'))
  print(
    htmltools::tagList(
    reportTableFormat(
      table = cmOutUnique[[cmi]],
      groupBy = "parentNameOutcome", 
      groupByButton = TRUE,
      columns = list(
        priorOutcomeLookback = reactable::colDef(
          aggregate = "unique",
          show = TRUE,
          name = 'Prior Outcome Lookback (days)',
          filterable = TRUE
        ),
        outcomeId = reactable::colDef(show = FALSE),
        outcomeOfInterest = reactable::colDef(show = FALSE),
        subsetIdOutcome = reactable::colDef(show = FALSE),
        parentNameOutcome = reactable::colDef(
          show = TRUE,
          name = 'Outcome Parent',
          filterable = TRUE,
          html = TRUE, 
          minWidth = 300
        ),
        cohortNameOutcome = reactable::colDef(
          show = TRUE,
          name = 'Outcome',
          html = TRUE,
          filterable = TRUE, 
          minWidth = 300
          ),
        cohortNameWithLinkOutcome = reactable::colDef(
          show = FALSE,
          name = 'Outcome',
          html = TRUE,
          filterable = TRUE
        ),
        isParentOutcome = reactable::colDef(show = F),
        parentIdOutcome = reactable::colDef(show = F),
        subsetNameOutcome = reactable::colDef(show = F),
        packageVersionOutcome = reactable::colDef(show = F),
        numberSubsetOperatorsOutcome = reactable::colDef(show = F),
        subsetCohortsOutcome = reactable::colDef(show = F),
        appliedSubsetsOutcome = reactable::colDef(show = F)
      ),
    elementId = paste0("cm-out-tab-",cmi)
    )
    )
  )
  cat('\n:::\n')
}

cat('\n#### Excluded Covariates \n')  
cat('\n##### Shared Excluded Covariate Concept Ids {#sec-cm-exclude-0}\n') 
cat('\n::: {.callout-important collapse="true"}\n')
cat(paste0('\n# Shared excluded covariates used in cohort method \n'))
concepts <- ProtocolGenerator::getConcepts(
  conceptIds = commonExclude, 
  baseUrl = params$webAPI
    ) 

if(length(concepts$standard) > 0){
  cat('\n\n::: {.panel-tabset}\n\n')
cat('\n###### Standard \n')
 print(
   htmltools::tagList(
    reportTableFormat(
      table = concepts$standard %>% 
        dplyr::select("conceptId","conceptName", "domainId", "vocabularyId","conceptClassId"),
      columns = list(
        conceptName = reactable::colDef(filterable = TRUE),
        domainId = reactable::colDef(filterable = TRUE),
        vocabularyId = reactable::colDef(filterable = TRUE)
      )
    )
   )
 )

 cat('\n###### Source \n')
  print(
   htmltools::tagList(
 reportTableFormat(
      table = concepts$source %>% 
        dplyr::select("conceptId","conceptName", "domainId", "vocabularyId", "conceptClassId"),
      columns = list(
        conceptName = reactable::colDef(filterable = TRUE),
        domainId = reactable::colDef(filterable = TRUE),
        vocabularyId = reactable::colDef(filterable = TRUE)
      )
    )
   )
  )
  cat('\n\n:::\n\n')
} # length standard
cat('\n:::\n')

# add the commonExclude  commonNegativeId 

  for(ncsInd in 1:length(nonCommonSets)){
  
    cat(paste0('\n##### Excluded Covariate Concept Ids Set ',ncsInd,' {#sec-cm-exclude-',ncsInd,'} \n'))
   cat('\n::: {.callout-important collapse="true"}\n')
  cat(paste0('\n# Excluded covariates in cohort method ', ncsInd, '\n'))

concepts <- ProtocolGenerator::getConcepts(
  conceptIds = nonCommonSets[[ncsInd]], 
  baseUrl = params$webAPI
    ) 
  
if(length(concepts$standard) > 0){
 cat('\n\n::: {.panel-tabset}\n\n')
 cat('\n##### Standard \n')
 print(
   htmltools::tagList(
    reportTableFormat(
      table = concepts$standard %>% 
        dplyr::select("conceptId","conceptName", "domainId", "vocabularyId","conceptClassId"),
      columns = list(
        conceptName = reactable::colDef(filterable = TRUE),
        domainId = reactable::colDef(filterable = TRUE),
        vocabularyId = reactable::colDef(filterable = TRUE)
      )
    )
   )
 )

 cat('\n##### Source \n')
  print(
   htmltools::tagList(
 reportTableFormat(
      table = concepts$source %>% 
        dplyr::select("conceptId","conceptName", "domainId", "vocabularyId", "conceptClassId"),
      columns = list(
        conceptName = reactable::colDef(filterable = TRUE),
        domainId = reactable::colDef(filterable = TRUE),
        vocabularyId = reactable::colDef(filterable = TRUE)
      )
    )
   )
  )
  cat('\n\n:::\n\n')
} else{
  cat('\nNone\n')
} 
cat('\n:::\n')
} # for loop

  cat('\n#### Shared Negative Controls {#sec-cm-negset-0}\n')
  cat('\n::: {.callout-important collapse="true"}\n')
  cat(paste0('\n# Shared negative controls in cohort method \n'))
  cat(paste0('A total of ',length(unique(commonNegativeId)),' negative controls were included accross analyses. \n'))
  
  print(
    htmltools::tagList(
    reportTableFormat(
      table = merge(
        data.frame(
          cohortId = commonNegativeId
        ), 
        negativeControlsCM, 
        by = 'cohortId', 
        all.x = T
        ) %>% dplyr::arrange(.data$cohortName), 
      groupBy = NULL, 
      columns = list(
        cohortName = reactable::colDef(
          name = 'Negative Control', 
          filterable = TRUE
        ),
        cohortId = reactable::colDef(show = FALSE),
        outcomeConceptId = reactable::colDef(
          name = 'ConceptId'
        )
      )
      #caption = paste('Negative controls for setting ',i)
    )
  )
  )
  cat('\n:::\n')
  
  # TODO add similar check for excluded covs?
  if(length(nonCommonNegSets) != 1 & length(nonCommonNegSets[[1]]) != 0){
    # add Negative controls that are different 
     for(ncsInd in 1:length(nonCommonNegSets)){
  
    cat(paste0('\n#### Negative Controls Set ',ncsInd,' {#sec-cm-negset-',ncsInd,'} \n')) 
    cat('\n::: {.callout-important collapse="true"}\n')
    cat(paste0('\n# Negative control set ',nscInd,' in cohort method \n'))
    
    print(
    htmltools::tagList(
    reportTableFormat(
      table = merge(
        data.frame(
          cohortId = nonCommonNegSets[[ncsInd]]
        ), 
        negativeControlsCM, 
        by = 'cohortId', 
        all.x = TRUE
        ), 
      groupBy = NULL, 
      columns = NULL
      #caption = paste('Negative controls for setting ',i)
    )
  )
  )
  cat('\n:::\n')
     }
  }
  

```

### Analysis Settings {#sec-cm-analyses}

```{r, echo=FALSE, results = 'asis'}

for(i in 1:length(analysisCm)){
  
  analysisSetting <- analysisCm[[i]]
  
  cat(paste0('\n#### Analysis ', analysisSetting$analysisId,': ', analysisSetting$description, ' \n'))
    
    cat('\n::: {.callout-important collapse="true"}\n')
    cat(paste0('\n# Setting getDbCohortMethodData in cohort method \n'))
    
    cat(getHelpText(
    package = 'CohortMethod',
    functionName = 'getDbCohortMethodData',
    input = NULL))
  
  covariateSettings <- analysisSetting$getDbCohortMethodDataArgs$covariateSettings
  
  analysisSetting$getDbCohortMethodDataArgs$covariateSettings <- NULL
  
  extractSettings <- getSettingsTable(
  package, 
  functionName = 'createGetDbCohortMethodDataArgs', 
  settings = analysisSetting$getDbCohortMethodDataArgs
)
  if(!is.null(covariateSettings)){
    covariateDetails <- formatCovariateSettings(covariateSettings)
  } else{
    covariateDetails <- NULL
  }
  
  print(
    shiny::tagList(
  reportTableFormat(
      table = rbind(
        extractSettings,
        covariateDetails
        ),
      columns = append(defaultColumns(covariateDetails),
                       list(
                       desc = reactable::colDef(
                         name = 'Description', 
                         minWidth = 300
                         )
                     ))
    )
    )
  )
  cat('\n:::\n')

# print tables for the remaining components
cohortMethodComponents <- names(analysisSetting)
cohortMethodComponents <- cohortMethodComponents[!cohortMethodComponents %in% c('analysisId','description','getDbCohortMethodDataArgs', 'computeCovariateBalanceArgs')]

for(settingName in cohortMethodComponents){
  
  if(!is.null(analysisCm[[i]][[settingName]])){
  cat('\n::: {.callout-important collapse="true"}\n')
  cat(paste0('\n# Setting ',settingName,' in cohort method \n'))
  
  functionName <- getFunctionFromArgName(package, settingName)[1]
  
  if(!is.na(functionName)){ # what to do when NA?
  
  cat(
    getHelpText(
    package = package,
    functionName = functionName,
    input = NULL
), sep = '\n')
  
descAndDefault <- getAllHelpDetails(package, functionName)
settingDf <- getSettingsTable(
  package = package, 
  functionName = functionName, 
  settings = analysisCm[[i]][[settingName]]
  )

  print(
    shiny::tagList(
    reportTableFormat(
      table = settingDf,
    columns = append(defaultColumns(settingDf),
                     list(
                       desc = reactable::colDef(
                         name = 'Description', 
                         minWidth = 300
                         )
                     ))
    )
  )
  )
    
      
  } else{
    cat('No settings to display')
  }
  cat('\n:::\n')
  
  }
}

# manually adding computeCovariateBalanceArgs
if('computeCovariateBalanceArgs' %in% names(analysisCm[[i]])){
  if(!is.null(analysisCm[[i]]$computeCovariateBalanceArgs)){
cat('\n::: {.callout-important collapse="true"}\n')
cat(paste0('\n# Setting computeCovariateBalanceArgs in cohort method \n'))    
  settingName <- 'computeCovariateBalanceArgs'
  functionName <- getFunctionFromArgName(package, settingName)[1]
  
  if(!is.na(functionName)){ # what to do when NA?
  
  cat(
    getHelpText(
    package = package,
    functionName = functionName,
    input = NULL
), sep = '\n')
    
    covariateFilter <- analysisCm[[i]][[settingName]]$covariateFilter
    analysisCm[[i]][[settingName]]$covariateFilter <- NULL
  
descAndDefault <- getAllHelpDetails(package, functionName)
settingDf <- getSettingsTable(
  package = package, 
  functionName = functionName, 
  settings = analysisCm[[i]][[settingName]]
  )

  print(
    shiny::tagList(
    reportTableFormat(
      table = settingDf,
    columns = append(defaultColumns(settingDf),
                     list(
                       desc = reactable::colDef(
                         name = 'Description', 
                         minWidth = 300
                         )
                     )
    )
    )
  )
  )
  
  if(is.data.frame(covariateFilter)){
    cat("\n covariateFilter Settings: \n")
    print(
    shiny::tagList(
    reportTableFormat(
      table = covariateFilter
    )
    )
    )
  }
  
  cat('\n:::\n')
  
  }
  } # if "computeCovariateBalanceArgs" not NULL
} # if "computeCovariateBalanceArgs"


  
}


```

### Global Settings

::: {.callout-important collapse="false"}
# Global settings in cohort method

The following settings are used when running the analysis and apply to all CohortMethod analyses.

```{r, echo=FALSE, results = 'asis'}

    reportTableFormat(
      table = data.frame(
        input = c('refitPsForEveryOutcome','refitPsForEveryStudyPopulation'),
        description = c(
          getHelpText(
    package = package,
    functionName = 'createCmAnalysesSpecifications',
    input = 'refitPsForEveryOutcome'
), 
getHelpText(
    package = package,
    functionName = 'createCmAnalysesSpecifications',
    input = 'refitPsForEveryStudyPopulation'
)
),
        value = c(
          refitPsForEveryOutcome,
          refitPsForEveryStudyPopulation
        )
    ),
    groupBy = NULL, columns = NULL
    )
  

```
:::

### Diagnostics
::: {.callout-important collapse="false"}
# Diagnostics settings in cohort method

```{r, echo=FALSE, results = 'asis'}

if(!is.null(diagSetting)){
 
  diagSettings <- getSettingsTable(
    package = package,
    functionName = 'createCmDiagnosticThresholds',
    settings  = diagSetting
) 
 
print(
    htmltools::tagList(
      reportTableFormat(
      table = diagSettings,
      columns = append(defaultColumns(diagSettings),
                       list(
                       desc = reactable::colDef(
                         name = 'Description', 
                         minWidth = 300
                         )
                     ))
    )
    )
   )
}
  

```
:::


```{r cm_cohort_tracker, echo=FALSE, results = 'asis',include=FALSE}

# code to get the targets and outcomes for c
# and add to the cohortTracker

cmOuts <- unique(unlist(lapply(cmOutUnique, function(x) x$outcomeId)))

cohortTracker <- rbind(
  cohortTracker,
  data.frame(
  type = c(
    rep('cmTarget', length(unique(tcCombos$targetId))),
    rep('cmOutcome', length(cmOuts)),
    rep('cmComp', length(unique(tcCombos$comparatorId)))
    ),
  cohortId = c(unique(tcCombos$targetId), cmOuts, unique(tcCombos$comparatorId)),
  value = 1
  )
)

```
