---
output: html_document
---

## Cohort Incidence

### Overview

::: {.callout-important collapse="false"}
# Summary of cohort incidence
Cohort Incidence calculates the incidence proportion (per 100 patients) and incidence rate (per 100 patient years) for a set of target cohorts, outcomes (with a specified washout) and time-at-risks. Stratification of the target cohorts by age group, gender and index year is also possible.

The incidence proportion shows how often a patient in the target population has the outcome observed during the time-at-risk divided by the number of patients in the target population multiplied by 100 (to get it per 100 patients). The results contain the number of patients in the target population, the number of patients in the target population with the outcome observed during the time-at-risk and the incidence proportion.

The incidence rate is calculated as the number of times the outcome is observed during a time-at-risk period for the target population divided by the number of days at risk for all patients in the target population divided by 365 (to get per year) and multiplied by 100 (to get per 100 years). The results contain the total number of days at risk for all patients in the target population, the number of times an outcome occurs during a time at risk and the incidence rate.

Cohort incidence can enable multiple time-at-risk periods per patient but the outcome washout is used to remove periods of time where it is impossible to observed an outcome. For more details of cohort incidence see [here](https://ohdsi.github.io/CohortIncidence/articles/cohortincidence-method-documentation.html).

```{r, echo=FALSE, results = 'asis',include=FALSE}

# get analysisList
analysisList <- CohortIncidenceModuleSettings$settings$irDesign$analysisList

# create count sentances for each analysis
countSentances <- ProtocolGenerator::getCountStatement(
    CohortIncidenceModuleSettings = CohortIncidenceModuleSettings,
    cohortDefinitionDf = cohortDefinitionDf
    )

# stratification sentance
stratSentance <- ProtocolGenerator::createStratSentance(CohortIncidenceModuleSettings)

```

The incidence rate specification contains `r length(analysisList)` analysis settings consisting of combinations of target cohorts, outcomes and time at risk (TAR) settings. The stratification settings are shared across analyses.

```{r, echo=FALSE, results = 'asis'}
cat(stratSentance, sep = '\n')
cat('\n')
cat('The analysis settings are:', sep = '\n')
cat('\n')
cat(unlist(countSentances), sep = '\n')
cat('\n')
```

:::

```{r, echo=FALSE, results = 'asis'}

# column settings for the target and outcome tables
ciColumns <- ProtocolGenerator::getCIcolumns()
# the target and outcome tables plus tar per setting and target/outcome vectors
ciTargetsOutcomes <- ProtocolGenerator::getCiTargetsOutcomes(CohortIncidenceModuleSettings, cohortDefinitionDf)

for(i in 1:length(analysisList)){

  cat(
    paste0(
      "\n### Analysis ", i, "{#sec-incidence-analysis-",i,"} \n")
    )
  
   cat('\n\n')
   cat(paste0("#### Targets{#sec-incidence-t-",i,"}\n"))
   
  if(nrow(ciTargetsOutcomes$ciTargets[[i]])>0){ 
      cat('\n::: {.callout-important collapse="true"}\n')
      cat(paste0("# Target cohorts included in cohort incidence\n"))
      cat('\nA table with the target cohorts group by parent cohort:\n')
 print(shiny::tagList(
   ProtocolGenerator::reportTableFormat(
    table = ciTargetsOutcomes$ciTargets[[i]] %>%
      dplyr::arrange(.data$parentName,.data$cohortName), # always have parentName?
    groupBy = "parentName", 
    groupByButton = TRUE,
    elementId = 'ci-targets',
    columns = ciColumns[names(ciColumns) %in% colnames(ciTargetsOutcomes$ciTargets[[i]])], 
    caption = 'Target cohorts included in cohort incidence.'
    )))
  cat('\n:::\n')
   cat('\n\n')
  }
  
  cat(paste0("\n\n#### Outcomes {#sec-incidence-o-",i,"}\n"))
   if(!is.null(ciTargetsOutcomes$ciOutcomes[[i]])){ # 
      cat('\n::: {.callout-important collapse="true"}\n')
      cat(paste0("# Outcome cohorts included in cohort incidence\n"))
      cat('\nA table with the outcome cohorts group by parent cohort:\n')
print(shiny::tagList(ProtocolGenerator::reportTableFormat(
    table = ciTargetsOutcomes$ciOutcomes[[i]] %>%
      dplyr::arrange(.data$parentName,.data$cohortName), 
    groupBy = "parentName", 
    groupByButton = TRUE,
    columns = ciColumns[names(ciColumns) %in% colnames(ciTargetsOutcomes$ciOutcomes[[i]])],
    caption = 'Outcome cohorts included in cohort incidence.', 
    elementId = 'ci-out-tab'
)))
 cat('\n:::\n')
 cat('\n\n')
}
  
  cat(paste0("\n\n#### Time-at-risks (TARs) {#sec-incidence-tar-",i,"}\n"))
      cat('\n::: {.callout-important collapse="true"}\n')
      cat(paste0("# Time-at-risks included in cohort incidence\n"))
      cat(ciTargetsOutcomes$tars[[i]])
      cat('\n:::\n')
      cat('\n\n')
}
  
   cat("\n### Stratification {#sec-incidence-strat}\n", sep ='\n')
   
   strataTable <- ProtocolGenerator::getSettingsTable(
  package = 'CohortIncidence', 
  functionName = 'createStrataSettings',
  settings = as.list(sapply(CohortIncidenceModuleSettings$settings$irDesign$strataSettings, function(x) paste(x, sep = ',', collapse = ','))) 
)
 cat('\n\n')
 
     cat('\n::: {.callout-important collapse="true"}\n')
     cat(paste0("# Stratification settings in cohort incidence\n"))
     print(shiny::tagList(reportTableFormat(
      table = strataTable, 
      columns = defaultColumns(strataTable),
      caption = 'Stratification settings'
      )))
      cat('\n:::\n')
      cat('\n\n')
  
```

```{r ci_cohort_tracker, echo=FALSE, results = 'asis',include=FALSE}

# code to get the targets and outcomes for ci
# and add to the cohortTracker
cohortTracker <- rbind(
  cohortTracker,
  data.frame(
  type = c(
    rep('ciTarget', length(unique(ciTargetsOutcomes$ciTargetIds))),
    rep('ciOutcome', length(unique(ciTargetsOutcomes$ciOutcomeIds)))
    ),
  cohortId = c(unique(unlist(ciTargetsOutcomes$ciTargetIds)), unique(unlist(ciTargetsOutcomes$ciOutcomeIds))),
  value = 1
  )
)

```
