---
output: html_document
---

```{r, echo=FALSE, results = 'asis', include=FALSE}

cdTables <- ProtocolGenerator::getCohortDiagnosticTables(
  CohortDiagnosticsSettings = CohortDiagnosticsSettings,
  cohortDefinitionDf = cohortDefinitionDf
)

cdColumns <- ProtocolGenerator::getCdCols()

```

## Cohort Diagnostics

::: {.callout-important collapse="false"}
# Summary of cohort diagnostics
Cohort diagnostics is used to evaluate phenotypes. See [here](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0310634) for more details.

Cohort diagnostics is a set of automated checks that summarizes who a phenotype algorithm selects as having a medical condition or drug exposure (their age, sex, diagnoses, tests, and treatments). It helps researchers spot mistakes or unexpected results so they can be confident the people included in a cohort really match the condition or drug being studied.

:::

### Cohorts

::: {.callout-important collapse="true"}
# Cohorts used in cohort diagnostics
Cohort diagnostics will be run for the following `r nrow(cdTables$targetTable)` cohorts:

```{r, echo=FALSE, results = 'asis'}
 print(shiny::tagList(
   ProtocolGenerator::reportTableFormat(
    table = cdTables$targetTable %>%
      dplyr::arrange(.data$parentNameTarget,.data$cohortNameTarget), 
    groupBy = 'parentNameTarget', 
    groupByButton = TRUE, 
    elementId = 'cd-cohorts',
    columns = cdColumns[names(cdColumns) %in% colnames(cdTables$targetTable)], 
    caption = 'Cohorts included in Cohort Diagnostics.'
    )))
```
:::

### Settings

::: {.callout-important collapse="true"}
# Main settings
The following cohort diagnostic settings are used:

```{r, echo=FALSE, results = 'asis'}
 print(shiny::tagList(
   ProtocolGenerator::reportTableFormat(
    table = cdTables$settingsTable, 
    caption = 'Settings.'
    )))
```
:::

::: {.callout-important collapse="true"}
# Temporal feature settings:

```{r, echo=FALSE, results = 'asis'}
 print(shiny::tagList(
   ProtocolGenerator::reportTableFormat(
    table = cdTables$featureTable, 
    caption = 'Feature Settings.'
    )))
```

::: 


```{r cd_cohort_tracker, echo=FALSE, results = 'asis',include=FALSE}

# code to get the targets for cd
# and add to the cohortTracker

if(length(cdTables$targetTable$cohortId) > 0 ){
cohortTracker <- rbind(
  cohortTracker,
  data.frame(
  type = c(
    rep('cdTarget', length(unique(cdTables$targetTable$cohortId)))
    ),
  cohortId = unique(cdTables$targetTable$cohortId),
  value = 1
  )
)
}

```
