---
output: html_document
---

```{r, echo=FALSE, result = 'asis'}

plpSettings <- ProtocolGenerator::getPlpSettings(
  PatientLevelPredictionModuleSettings = PatientLevelPredictionModuleSettings,
  cohortDefinitionDf = cohortDefinitionDf
)

tos <- plpSettings$targetOutcomeSet
modelDesignUnique <-  plpSettings$modelDesignUnique
predictionSummary <- plpSettings$predictionSummary

plpColDefs <- ProtocolGenerator::getPlpColDefs()

```
  
## PatientLevelPrediction

This analysis develops binary classifiers for a given patient population that predict the risk of a patient developing some outcome during some time at risk relative to prediction index.  These models are useful if you want to implement some intervention and would like to identify a 'high risk' group of patients who may benefit most from the intervention.  

There is a total of ``r length(modelDesignUnique)`` patient level prediction model designs specified, see @sec-model-designs.  The table below contains links to the model designs that show the table of target and outcome pairs and the model specification.  The table also summarizes the time-at-risk for each model design and the covariate settings.

::: {.callout-important collapse="false"}
# Table of model designs
```{r, echo=FALSE, result = 'asis'}

reportTableFormat(
  table = predictionSummary, 
  columns = plpColDefs
  )
  
```
:::

### Output

::: {.callout-important collapse="false"}
# Outputs of patient-level prediction
The following are the standardized metrics used to evaluate patient-level prediction models.

```{r, echo=FALSE, result = 'asis'}
modelEvaluation <- data.frame(rbind(
    c("AUROC", "Discrimination", "The Area Under the Receiver Operating Characteristic curve is a common discrimination metric.  It corresponds to the probability that a randomly selected patient with the outcome is assigned a higher risk by the model than a randomly selected patients without the outcome."),
    
    c("AUPRC", "Discrimination", "The Area Under the Precision Recall curve is a common discrimination metric that provides a useful insight when the outcome is rare."), 
    
    c("Calibration-in-the-large", "Calibration" , "A measure of how well the predicted risk matches the observed risk on average.  It compares the mean predicted risk for the whole popualtion (the model's predicted risk) with the observed risk (the true risk)"),
    
  c("E-statistic", "Calibration" , "A measure corresponding to the average difference between the true risk and the predicted risk.")
    
    )
  )
  names(modelEvaluation) <- c("Name", "Type","Description")
  row.names(modelEvaluation) <- NULL
  data <- modelEvaluation[order(modelEvaluation$Type),]
  
  reportTableFormat(
    table = data, 
    caption = 'Prediction Metrics'
  )
  
  
```
:::

### Model Design {#sec-model-designs}
```{r results='asis', echo=FALSE}
    for (i in 1:length(modelDesignUnique)) {
      modelDesignSetting <- modelDesignUnique[[i]]
      tosSub <- tos[tos$designId == i,]
      modelDesign <- knitr::knit_child("prediction/model-design.Rmd", quiet = TRUE, envir = environment())
      cat(modelDesign, sep = '\n')
    }
```



```{r plp_cohort_tracker, echo=FALSE, results = 'asis',include=FALSE}

# code to get the targets and outcomes for c
# and add to the cohortTracker

cohortTracker <- rbind(
  cohortTracker,
  data.frame(
  type = c(
    rep('plpTarget', length(unique(tos$cohortIdTarget))),
    rep('plpOutcome', length(unique(tos$cohortIdOutcome)))
    ),
  cohortId = c(unique(tos$cohortIdTarget), unique(tos$cohortIdOutcome)),
  value = 1
  )
)

```
