---
output: html_document
---
  
```{r sccs_settings, echo=FALSE, results = 'hide', include = FALSE}

package <- "SelfControlledCaseSeries"

sccsSettings <- ProtocolGenerator::getSccsSettings(
  SelfControlledCaseSeriesModuleSettings = SelfControlledCaseSeriesModuleSettings,
    cohortDefinitionDf = cohortDefinitionDf,
    negativeControls = negativeControls
    )
sccsColDefs <- ProtocolGenerator::getSccsColDefs()

eoOfInt <- sccsSettings$eoOfInt
negTabShared <- sccsSettings$negTabShared
negTab <- sccsSettings$negTab
  
```

## Self Controlled Case Series 

### Overview
::: {.callout-important collapse="false"}
# Summary of self controlled case series
The self controlled case series aims to determine whether there is an effect between a drug and outcome.  The self controlled case series compares exposure time with unexposed time to see whether the outcome is more likely to occur while exposed. 

The design requires the user to specify the target population of interest, an optional indication to restrict to and the outcome of interest.  Similar to cohort method, diagnostics to implemented to identify potential bias and effect estimates are only unblinded if all diagnostics pass.

In this specification there are ``r length(unique(eoOfInt$parentIdTarget))`` unique parent exposure cohorts (``r nrow(unique(eoOfInt[, c('exposureId', 'nestingId')]))`` unique exposure and indications combinations), see @sec-sccs-eo.  There is a total of ``r length(unique(eoOfInt$nestingId))`` unique indications.  A total of ``r length(unique(eoOfInt$parentIdOutcome))`` parent outcome cohorts (``r length(unique(eoOfInt$outcomeId))`` unique outcomes with subsets).

In total there are ``r length(sccsSettings$sccsAnalysisList)`` different self controlled case series analysis designs (see @sec-sccs-analysis).

:::

### Exposure Indication Outcomes {#sec-sccs-eo}

::: {.callout-important collapse="true"}
# Outcome exposure pairs of interest included in sccs
```{r sccs_exposure_outcomes, echo=FALSE, results = 'asis'}

reportTableFormat(
  table = eoOfInt %>% 
    dplyr::select(-c("trueEffectSize", "exposureIdRef")) %>%
    dplyr::arrange(.data$parentNameTarget, .data$cohortNameWithLinkOutcome), 
  groupBy = 'parentNameTarget', # or outcome?
  columns = sccsColDefs,
  elementId = 'sccs-eio',
  groupByButton = TRUE,
  caption = 'Outcome exposure pairs of interest included in study'
  )
cat('\n\n')

```
:::

### Negative Outcomes 

```{r negative_control_table, echo=FALSE, results = 'asis'}

if(!is.null(negTabShared)){
cat('\n\n')
cat(paste("A total of ", length(unique(negTabShared$outcomeName)), " negative control outcomes were shared across all the analyses\n\n"), sep = '\n\n')
cat('\n\n')

if(!"standardConcept" %in% colnames(negTabShared)){
  negTabShared$standardConcept <- ''
}

cat('\n::: {.callout-important collapse="false"}\n')
cat('\n# Negative controls shared in sccs\n')
print(shiny::tagList(reportTableFormat(
  table = negTabShared %>%
    dplyr::select("outcomeName", "standardConcept") %>%
    dplyr::relocate("outcomeName", .before = "standardConcept"),
  columns = list(
    outcomeName = reactable::colDef(
          name = 'Negative Control Outcome',
          html = TRUE, 
          filterable = T, 
          minWidth = 200
          )
  ),
  caption = 'Negative outcomes shared across the study'
  )))

cat('\n:::\n')
cat('\n\n')

} # end NegTabShared


if(!is.null(negTab)){

cat('\n::: {.callout-important collapse="true"}\n')
cat('\n# Negative controls per analysis in sccs\n')

reportTableFormat(
  table = negTab,
  groupBy = 'setting',#c('outcomeName', 'exposureName'),
  columns = list(
        setting = reactable::colDef(
          name = 'Negative Control Setting'
        ),
    outcomeName = reactable::colDef(
          name = 'Outcome',
          html = TRUE, 
          filterable = TRUE
          ),
    exposureName = reactable::colDef(
          name = 'Exposure',
          html = TRUE, 
          filterable = TRUE
          )
    
  ),
  caption = 'Negative outcome included in study per setting'
  )
cat('\n:::\n')
cat('\n\n')

} # end NegtabNotShared

```

### Analyses {#sec-sccs-analysis}
```{r sccs_analyses, echo=FALSE, results = 'asis'}


for(i in 1:length(sccsSettings$sccsAnalysisList)){
  
  analysisSetting <- sccsSettings$sccsAnalysisList[[i]]
    
  cat(
    paste0('#### Analysis ', analysisSetting$analysisId,': ', analysisSetting$description, ' \n'), 
    sep = '\n'
    )
  
   #cat("\n::: panel-tabset\n")
  for( settingName in names(analysisSetting)[-which(names(analysisSetting) %in% c('analysisId','description','createIntervalDataArgs') )] ){
    
    functionName <- getFunctionFromArgName(package, settingName)
    
    cat('\n::: {.callout-important collapse="true"}\n')
    cat(paste0('\n# Setting ',settingName,' used in sccs\n'))
    
   cat(getHelpText(
    package = 'SelfControlledCaseSeries',
    functionName = functionName,
    input = NULL
), sep = '\n')
    
descAndDefault <- getAllHelpDetails(package, functionName)
settingDf <- getSettingsTable(
  package = package, 
  functionName = functionName, 
  settings = analysisSetting[[settingName]]
  )

  print(
    htmltools::tagList(
    reportTableFormat(
      table = settingDf,
      #groupBy = "input",
    columns = append(defaultColumns(settingDf),
                     list(
                       desc = reactable::colDef(
                         name = 'Description', 
                         minWidth = 300
                         )
                     ))
    )
  )
  )
   cat('\n:::\n') 
  }
  
  # analysisSetting$createIntervalDataArgs
  cat('\n::: {.callout-important collapse="true"}\n')
  cat(paste0('\n# Setting createIntervalDataArgs used in sccs\n'))
   cat(
   getHelpText(
    package = package,
    functionName = 'createSccsIntervalData',
    input = NULL
), sep ='\n'
)
   
   allData <- getSettingsTable(
  package = package, 
  functionName = 'createCreateSccsIntervalDataArgs', 
  settings = list(
    minCasesForTimeCovariates = analysisSetting$createIntervalDataArgs$minCasesForTimeCovariates,
    eventDependentObservation = analysisSetting$createIntervalDataArgs$eventDependentObservation
  )
)
   
   # in new R6 the way to check a list of settings is to see if the names are null
   # so here I check for the class (old way) or not null names (R6 way)
  if(inherits(analysisSetting$createIntervalDataArgs$eraCovariateSettings, "EraCovariateSettings") || !is.null(names(analysisSetting$createIntervalDataArgs$eraCovariateSettings)) ){
    analysisSetting$createIntervalDataArgs$eraCovariateSettings <- list(analysisSetting$createIntervalDataArgs$eraCovariateSettings)
  }
  for(l in 1:length(analysisSetting$createIntervalDataArgs$eraCovariateSettings)){
    ecs <- analysisSetting$createIntervalDataArgs$eraCovariateSettings[[l]]
  
    allData <- rbind(
      allData,
      getSettingsTable(
    package = package,
    functionName = 'createEraCovariateSettings',
    settings  = analysisSetting$createIntervalDataArgs$eraCovariateSettings[[l]]
) %>% dplyr::mutate("level2" = .data$input) %>%
  dplyr::mutate("input" = paste0('eraCovariateSettings ', l))
)
    
  }
   if(!is.null(analysisSetting$createIntervalDataArgs$calendarTimeCovariateSettings)){
   if(inherits(analysisSetting$createIntervalDataArgs$calendarTimeCovariateSettings, "CalendarTimeCovariateSettings") || !is.null(names(analysisSetting$createIntervalDataArgs$calendarTimeCovariateSettings))){
    analysisSetting$createIntervalDataArgs$calendarTimeCovariateSettings <- list(analysisSetting$createIntervalDataArgs$calendarTimeCovariateSettings)
  }
  for(l in 1:length(analysisSetting$createIntervalDataArgs$calendarTimeCovariateSettings)){
    ctcs <- analysisSetting$createIntervalDataArgs$calendarTimeCovariateSettings[[l]]
    
     allData <- rbind(
      allData,
      getSettingsTable(
    package = package,
    functionName = 'createCalendarTimeCovariateSettings',
    settings  = ctcs
) %>% dplyr::mutate("level2" = .data$input) %>%
  dplyr::mutate("input" = paste0('calendarTimeCovariateSettings ', l))
)
    
  }
   }
   
   if(!is.null(analysisSetting$createIntervalDataArgs$ageCovariateSettings)){
   if(inherits(analysisSetting$createIntervalDataArgs$ageCovariateSettings, "AgeCovariateSettings") || !is.null(names(analysisSetting$createIntervalDataArgs$ageCovariateSettings))){
    analysisSetting$createIntervalDataArgs$ageCovariateSettings <- list(analysisSetting$createIntervalDataArgs$ageCovariateSettings)
  }
  for(l in 1:length(analysisSetting$createIntervalDataArgs$ageCovariateSettings)){
    acs <- analysisSetting$createIntervalDataArgs$ageCovariateSettings[[l]]
    
     allData <- rbind(
      allData,
      getSettingsTable(
    package = package,
    functionName = 'createAgeCovariateSettings',
    settings  = acs
) %>% dplyr::mutate("level2" = .data$input) %>%
  dplyr::mutate("input" = paste0('ageCovariateSettings ', l))
)
    
  }
   }
   
      if(!is.null(analysisSetting$createIntervalDataArgs$seasonalityCovariateSettings)){
   if(inherits(analysisSetting$createIntervalDataArgs$seasonalityCovariateSettings, "SeasonalityCovariateSettings") || !is.null(names(analysisSetting$createIntervalDataArgs$seasonalityCovariateSettings))){
    analysisSetting$createIntervalDataArgs$seasonalityCovariateSettings <- list(analysisSetting$createIntervalDataArgs$seasonalityCovariateSettings)
  }
  for(l in 1:length(analysisSetting$createIntervalDataArgs$seasonalityCovariateSettings)){
    scs <- analysisSetting$createIntervalDataArgs$seasonalityCovariateSettings[[l]]
    
     allData <- rbind(
      allData,
      getSettingsTable(
    package = package,
    functionName = 'createSeasonalityCovariateSettings',
    settings  = scs
) %>% dplyr::mutate("level2" = .data$input) %>%
  dplyr::mutate("input" = paste0('seasonalityCovariateSettings ', l))
)
    
  }
   }
  
   print(
    htmltools::tagList(
      reportTableFormat(
      table = allData, 
      columns = append(defaultColumns(allData),
                       list(
                       desc = reactable::colDef(
                         name = 'Description', 
                         minWidth = 300
                         )
                     ))
    )
    )
   )
   cat('\n:::\n') 
   #cat("\n:::\n")
}

```

### Diagnostics

```{r sccs_diagnostics, echo=FALSE, results = 'asis'}

  cat('\n::: {.callout-important collapse="false"}\n')
  cat(paste0('\n# Diagnostics used in sccs \n'))
    
if('sccsDiagnosticThresholds' %in% names(sccsSettings)){
 diagSetting <- sccsSettings$sccsDiagnosticThresholds
 
  diagSettings <- getSettingsTable(
    package = package,
    functionName = 'createSccsDiagnosticThresholds',
    settings  = diagSetting
) 
 
print(
    htmltools::tagList(
      reportTableFormat(
      table = diagSettings,
      columns = append(defaultColumns(diagSettings),
                       list(
                       desc = reactable::colDef(
                         name = 'Description', 
                         minWidth = 300
                         )
                     ))
    )
    )
   )
} else{
  cat('No settings found')
}
  
  cat('\n:::\n') 

```

```{r sccs_cohort_tracker, echo=FALSE, results = 'asis',include=FALSE}

# code to get the targets and outcomes for c
# and add to the cohortTracker
if(nrow(eoOfInt) > 0){
cohortTracker <- rbind(
  cohortTracker,
  data.frame(
  type = c(
    rep('sccsTarget', length(unique(eoOfInt$exposureId))),
    rep('sccsOutcome', length(unique(eoOfInt$outcomeId))),
    rep('sccsIndication', length(unique(eoOfInt$nestingId))) # what if 0?
    ),
  cohortId = c(unique(eoOfInt$exposureId), unique(eoOfInt$outcomeId) ,unique(eoOfInt$nestingId)),
  value = 1
  )
)
}

```
